Recurrence Quantification Analysis to quantify Movement Variability in Human-Humanoid Interaction Activities

### 2021-06-27 docs/manuscript/main.tex
provides statement for experimental protocol

A review of the way in which the project was conducted was undertaken by the Head of Research Governance at the University of Birmingham. 
An ethics position statement was prepared to confirm that ethical issues for this project were considered sufficiently to allow data from this project to be used for the research (ERN 21-0774).
This was approved in line with University processes.
%Refer to Appendix D for further information about the ethics, online participation information sheets and experiment check list.

>>>>

A review of the way in which the project was conducted was undertaken by the Head of Research Governance at the University of Birmingham. 
An ethics position statement was prepared to confirm that ethical issues for this project were considered sufficiently to allow data from this project to be used for the research.    
Hence the ethics position statement and experimental protocol was approved in line with the University of Birmingham processes (ERN 21-0774).
%Refer to Appendix D for further information about the ethics, online participation information sheets and experiment check list.
